### 2018-07-05 paper/4-build.tex
Another wibble in Section 4

The deep constructive trace approach only works if the operations are
\emph{deterministic}, otherwise it is possible to violate correctness resulting
in a so-called ``Frankenbuild''~\cite{esfahani2016cloudbuild}. Concretely, if
the result of building a key given a set of immediate dependencies can vary,
then it is possible that key \hs{k} will have been computed locally, but
something \emph{using} \hs{k} will have been taken as a constructive input using
a different value for \hs{k}. If another rule combines those two values then two
different values of \hs{k} will have been used in one rule, leading to problems
such as link-errors for typical compilers.

>>>>

The deep constructive trace approach only works if the operations are
\emph{deterministic}, otherwise it is possible to violate correctness.
Concretely, if
the result of building a key given a set of immediate dependencies can vary,
then it is possible that key \hs{k} will have been computed locally, but
something \emph{using} \hs{k} will have been taken as a constructive input using
a different value for \hs{k}. If another rule combines those two values then two
different values of \hs{k} will have been used in one rule, leading to problems
such as link-errors for typical compilers -- a phenomenon known as a
\emph{Frankenbuild}~\cite{esfahani2016cloudbuild}.
